---
title: 'Modeling Nikes Daily and Monthly Stock Returns [Period: 2007-2016]'
author: "Manav Dalmiya"
date: "4/2/2017"
output: html_document
---

Clear Memory + Import Packages
```{r}
rm(list=ls(all=TRUE))

library(stats)
library(zoo)
library(nortest)
library(tseries)
library(moments)
library(forecast)
library(rugarch)
library(FinTS)
```

###Nike Daily + Monthly Returns [Period: 2007-2016]: Import and Take Log Difference
```{r}
# Import Nike's Daily Returns
nike <- get.hist.quote(instrument = "nke", compression = "d", start = "2007-01-01", end = "2016-12-31", quote = "AdjClose", retclass = c("zoo"))

# Log Difference of Daily Returns
Nike_dailyret<-100*diff(log(nike))
```

###Nike Daily Returns: ARMA(p,q) using BIC

Nike's daily returns and squared daily returns reject the null hypothesis of no serial correlation (p < 0.05). There is evidence of ARCH at lags of 2, 7, and 28.
```{r}
auto.arima(Nike_dailyret, D=0, test=c("adf"), ic=c("bic"))
Box.test(Nike_dailyret, lag = 3, type = c("Ljung-Box"), fitdf = 0)
Box.test(Nike_dailyret^2, lag = 3, type = c("Ljung-Box"), fitdf = 0)
ArchTest(Nike_dailyret, lags=2, demean=TRUE)
ArchTest(Nike_dailyret, lags=7, demean=TRUE)
ArchTest(Nike_dailyret, lags=28, demean=TRUE)
```

###Estimate GARCH(1,1) Model for each error process using ARMA model

Nike - Daily Returns: GARCH(1,1)
```{r}
# Model Normal 1 - GARCH(1,1)
modN1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
mean.model = list(armaOrder = c(0, 0), include.mean = TRUE, archm = FALSE), distribution.model = "norm")
```

ARCH(0,0)
```{r}
modN1est_Nike<-ugarchfit(modN1, Nike_dailyret)
show(modN1est_Nike)
```


###Nike Daily Returns: Mean, Variance, Skewness, Kurtosis
```{r}
mean(Nike_dailyret)
var(Nike_dailyret)
skewness(Nike_dailyret)
kurtosis(Nike_dailyret)-3
rnike=coredata(Nike_dailyret)
shapiro.test(rnike)
ad.test(rnike)
jarque.bera.test(rnike)
```

```{r}
resids_Nike<-residuals(modN1est_Nike)
sigma_Nike<-sigma(modN1est_Nike)
nized_Nike<-resids_Nike/sigma_Nike
mean(nized_Nike)
var(nized_Nike)
skewness(nized_Nike)
kurtosis(nized_Nike)-3
shapiro.test(coredata(nized_Nike))
ad.test(coredata(nized_Nike))
jarque.bera.test(nized_Nike)
```

Nike: Daily Returns - Mean, Variance, Skewness, Kurtosis

The mean of Nike’s logged daily returns is 0.06220, which indicates that shares increased at a rate of 6.220%/day. The variance is 3.188, which is larger than var(normal dist.) = 1. The skewness is +0.2581, which indicates the daily returns are right skewed. The kurtosis is 7.590, which indicates the distribution is leptokurtic.

Nike GARCH(1,1): Daily Returns - Mean, Variance, Skewness, Kurtosis

The mean of Nike’s GARCH(1,1) model is -0.02857, which indicates that shares decreased at a rate of -2.857%/day. This is much lower than the non-GARCH model. The variance is 0.9965, which is approximately equal to var(normal dist.) = 1. The skewness is +0.3496, which indicates the GARCH daily returns are more rightly skewed than the non-GARCH model. The kurtosis is 8.258, which indicates the distribution is more leptokurtic than the non-GARCH model.

Nike: Shapiro-Wilk, Anderson-Darling, Jarque-Bera

Each test returns p-values < 2.2e-16. This supports the hypothesis that daily stock returns are serially uncorrelated.

Nike GARCH(1,1): Shapiro-Wilk, Anderson-Darling, Jarque-Bera

Each test returns p-values < 2.2e-16. This supports the hypothesis that the GARCH(1,1) daily stock returns are serially uncorrelated.



```{r}
estden_nike <- density(rnike, bw="SJ", kernel = c("epanechnikov"))
plot(estden_nike,main="Daily Nike Returns Density and Normal Density", col="blue")
xnike <- seq(min(rnike), max(rnike), 0.0001)
lines(xnike, dnorm(xnike, mean=mean(rnike), sd=sqrt(var(rnike))), lty="dashed")
```


```{r}
estden_Nike <- density(nized_Nike, bw="SJ", kernel = c("epanechnikov"))
plot(estden_Nike,main="Density of Normalised Resids. from GARCH(1,1) with Normal Cond. Dens.", col="blue")
x <- seq(-4, 4, 0.01)
lines(x, dnorm(x, mean=0, sd=1), lty="dashed")

```

Nike: Estimated Density against Normal Distribition.

As the kurtosis suggests, Nike’s estimated density function is leptokurtic with respect to the normal distribution.

Nike GARCH(1,1): Estimated Density against Normal Distribition.

The Nike GARCH(1,1)’s estimated density function has a smaller bandwidth than the non-GARCH mode. It is also much more leptokurtic than the non-GARCH model.

